`r params$doc_title`

### 2022-12-04 scripts/MSc.Rmd
modified plot sim

```{r updated-fig01, warning=FALSE}
plot_data1 <- df_cum_expl_var %>% 
  pivot_longer(cols = c(cum_expl_varX, cum_expl_varU, cum_expl_varY)) %>% 
  mutate(name = factor(name, labels = c("% var(U)", "% var(X)", "% var(Y)")),
         name = factor(name, levels = c("% var(X)", "% var(Y)", "% var(U)") )
         )

@@

```{r simulated-pves}
# EXPOSURE PVE
est_sim %>% 
  select(!!!(colname_pve_X)) %>% 
  pivot_longer(everything(), names_to = "PVE_X", values_to = "value_X") %>% 
  cbind(sample_size_filtered) %>% as_tibble() -> pve_X_sim

@@

```{r simulated-pves-raincloud-plot}

@@

>>>>

```{r updated-fig01, fig.height=6, fig.width=10, warning=FALSE}
plot_data1 <- df_cum_expl_var %>% 
  pivot_longer(cols = c(cum_expl_varX, cum_expl_varU, cum_expl_varY)) %>% 
  mutate(name = factor(name, labels = c("% var(U)", "% var(X)", "% var(Y)")),
         name = factor(name, levels = c("% var(X)", "% var(Y)", "% var(U)") )
         )

@@

```{r simulated-pves, fig.height=6, fig.width=10, warning=FALSE}
# EXPOSURE PVE
est_sim %>% 
  select(!!!(colname_pve_X)) %>% 
  pivot_longer(everything(), names_to = "PVE_X", values_to = "value_X") %>% 
  cbind(sample_size_filtered) %>% as_tibble() -> pve_X_sim

@@

```{r simulated-pves-raincloud-plot, fig.height=6, fig.width=10, warning=FALSE}

@@

plot_pve_simulated.raincloud
